Glaucoma Diagnosis Using Nerve Fiber Layer Thickness Images \\ Diagnóstico do Glaucoma Usando Imagens de Espessura da Camada de Fibras Nervosas

### 2018-10-21 Artigo WPGEC/Paper_WPGEC.tex
Final version

\renewcommand{\abstractname}{Abstract}
\begin{abstract}
Glaucoma is a cronic disease with slow progression and is characterized by the loss of the nerve fiber layer in the eye, if not treated it can lead to irreversible blindness.
The goal of this paper is to investigate the possibility of diagnosing glaucoma from nerve fiber layer thickness images using a convolutional neural network.
Using VGG16 and transfer learning technique, the net was initialized using pretrained weights for training and glaucoma classification on a dataset of images of nerve fiber layer thickness.
Initial results show that the use of OCT images in glaucoma diagnosis is viable, however, high loss on validation dataset suggests overfitting. One hypothesis for this result is the limited number of images in the training dataset.
\end{abstract}

>>>>

\renewcommand{\abstractname}{Abstract}
\begin{abstract}
Glaucoma is a chronic disease with slow progression
and is characterized by the loss of the nerve fiber layer in the eye.
If not treated it can lead to irreversible blindness.  The goal of
this paper is to investigate the possibility of diagnosing glaucoma
from images of thickness nerve fiber layer using a convolutional
neural network (CNN).  Using  VGG16 and transfer learning  technique,
the CNN was initialized using previously trained weights for training and
glaucoma classification on a dataset of images of nerve fiber
layer thickness. Initial results show that the use of OCT images
in glaucoma diagnosis is viable. However, high loss on validation
dataset suggests overfitting. One hypothesis for this result is the
limited number of images in the training dataset.
\end{abstract}
